% Dan Ramaley's Resume
% Based on Andrew McNabb's template.
% Created: 2005-04-13
% Updated: 2009-09-24
% Updated: 2011-02-06
% Updated: 2014-05-07

% To compile to an A4 PDF, first make sure a4paper is specified in the documentclass, then:
%     $ latex resume.tex
%     $ dvips -t a4 -Ppdf resume.dvi -o
%     $ ps2pdf resume.ps

\documentclass[11pt,oneside,a4paper]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
%\usepackage{url}
\usepackage{hyperref}

\pagestyle{empty}
\geometry{tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm,headheight=0cm,headsep=0cm,footskip=1cm}

\setlength{\parindent}{0cm}
\setlength{\parskip}{0cm}
\setlength{\itemsep}{0cm}
\setlength{\topsep}{0cm}
\setlength{\tabcolsep}{0cm}

% Name and contact information
\newcommand{\name}{Daniel A. Ramaley}
\newcommand{\addr}{1007 Kingman Circle, Des Moines IA 50311, USA}
\newcommand{\phone}{+1 (515) 271-5233}
\newcommand{\email}{dramaley@gmail.com}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}%\fontfamily{phv}\selectfont\Huge
	\huge % Font changed, size reduced from Huge to huge
	\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{4pt}
	{\large#1} % Font changed, size reduced from Large to large
	%{\fontfamily{phv}\selectfont\Large#1}
	\begin{itemize}
	\vspace{3pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt} % Change this to -4 if the resume needs to be tighter.
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\small\itshape \addr \hfill \phone; \email}

\vspace{8 pt}




%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Experience}

	\begin{ressubsec}{Office of Information Technology, Drake University}{Des Moines, IA, USA}{Network Programmer: 2005--present}
		\ressubitem{Led installation, maintenance, migration to and from, monitoring of, and documentation of most of Drake's key services (with up to 250,000 users), including:
			\begin{itemize}
			\ressubitem{40 Linux and 30 Solaris servers, making up the university's core infrastructure.}
			\ressubitem{Citrix XenServer virtual environment hosting 40 Linux and 65 Windows servers.}
			\ressubitem{Basic network services such as DHCP, DNS, NTP, and LDAP.}
			\ressubitem{Messaging/Collaboration services: Zimbra, Live@edu, Office 365, Google Docs.}
			\ressubitem{Web services leveraging multiple technologies such as the CMS, Apache, Tomcat, and Nginx to create \href{http://www.drake.edu/}{Drake's various} \href{http://news.drake.edu/}{online} \href{http://distinctly.drake.edu/}{presences}.}
			\ressubitem{Multiple \href{http://wlconline.drake.edu/}{WordPress} \href{http://wordpress.drake.edu/}{network} \href{http://oit.drake.edu/}{installations} used for teaching, training, and news.}
			\ressubitem{E-mail filtration which was 99\% effective at blocking or tagging spam and viruses.}
			\ressubitem{Backups for the entire server and desktop environments.}
			\end{itemize}
		}
		\ressubitem{Architected and developed bespoke software and contributed to open source projects:
			\begin{itemize}
			\ressubitem{An automated provisioning system to populate the campus LDAP, Active Directory, Google Docs, e-mail, and mailing lists.}
			\ressubitem{A self-service \href{https://pwgw.drake.edu/}{Password Gateway} for changing passwords and keeping them synchronized across multiple authentication sources.}
			\ressubitem{Rewrote \emph{NetReg}, the campus network registration system, to improve compliance with web standards and add numerous features. The ongoing enhancements submitted to the community are currently in use by approximately 30 organizations around the world.}
			\end{itemize}
		}
		\ressubitem{Trained other staff:
			\begin{itemize}
			\ressubitem{Co-developed a course on Git version control and helped train 6 developers.}
			\ressubitem{Currently developing a course to teach 8 people basic Unix/Linux usage.}
			\end{itemize}
		}
	\end{ressubsec}

	\begin{ressubsec}{Dice Career Solutions, Inc.}{Des Moines, IA, USA}{Software Engineer Consultant: 2010--2011}
		\ressubitem{Developed web spider software to scrape job postings off of partner web sites so they could be assimilated into Dice's central database.}
	\end{ressubsec}

	\begin{ressubsec}{Cowles Library, Drake University}{Des Moines, IA, USA}{System Administrator: 2001--2005}
		\ressubitem{Primary administrator of all information systems. Improved user experience through greater stability and security.}
		\ressubitem{Manage 100 Windows and 30 Mac OS X workstations and document their configuration.}
		\ressubitem{Maintain servers (Linux, OpenBSD, Solaris, Windows) and document their configuration.}
		\ressubitem{Develop tools and scripts to improve reliability and functionality of the network.}
		\ressubitem{Write CGI scripts, backup scripts, and other small utilities.}
		\ressubitem{Assist users with problems and write tutorials and documentation.}
	\end{ressubsec}

	\begin{ressubsec}{Visionary Systems, Ltd.}{Des Moines, IA, USA}{System Administrator and Developer: 2001}
		\ressubitem{Configured and maintained servers and web applications at a small start-up company geared to delivering custom software on tight deadlines.}
		\ressubitem{Wrote and maintained backup scripts to ensure business continuity.}
	\end{ressubsec}

	\begin{ressubsec}{Dial Center, Drake University}{Des Moines, IA, USA}{Student System Administrator: 2000}
		\ressubitem{Managed system configuration changes in a mission-critical environment.}
		\ressubitem{Defined and implemented security policies.}
	\end{ressubsec}

	\begin{ressubsec}{JPL, NASA}{Pasadena, CA, USA}{Intern: 1999}
		\ressubitem{Worked on Unix version of the \emph{WebWinds} data analysis and visualization tool.}
	\end{ressubsec}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Education and Certifications}

	\resitem{\textbf{Linux Certifications}
		\ressubitem{
Red Hat Certificate of Expertise in Server Hardening: Enterprise Linux 6, \#120-134-804\\*
Red Hat Certified  Engineer (RHCE): Enterprise Linux 6, \#120-134-804\\*
Red Hat Certified System Administrator (RHCSA): Enterprise Linux 6, \#120-134-804}
	}

	\begin{ressubsec}{Drake University}{Des Moines, IA, USA}{Bachelor of Science, Computer Science and in Mathematics, 2001\\*Bachelor of Fine Arts, Painting, 2006}
		\ressubitem{Minor in Physics}
		\ressubitem{Concentration in Sculpture}
	\end{ressubsec}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Skills}

	\resitem{\textbf{Operating Systems:} Linux (Debian, Red Hat, etc.), OpenBSD (2.5 to current), Solaris (8 to 11), Mac OS X, Windows}

	\begin{reslist}{Computer Languages:}
		\ressubitem{Proficient in Perl, Unix Shell, Regular expressions, HTML/XHTML}
		\ressubitem{Familiar with C, CSS, SQL, PHP, C++, \LaTeX, Scheme}
	\end{reslist}

	\begin{reslist}{Tools and Systems:}
		\ressubitem{Proficient in Apache, Bind, DHCPD, NTPD, LDAP, MySQL, Nginx, Postfix, PostgreSQL, Proofpoint, rsync, SSHD, Samba, WordPress, Zimbra}
		\ressubitem{Familiar with Avamar, DNSSEC, Git, iSCSI, Nagios, NFS, ProFTPD, Qmail, Sendmail, Shibboleth, Solaris Zones, SPF, Subversion, Terminal Four CMS, Tomcat, Varnish, ZFS}
	\end{reslist}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Achievements and Activities}

	\resitem{Currently studying Japanese (2006--present).}
	\resitem{Developed a \href{http://www.ramaley.net/cgi-bin/kana}{web-enabled r\=omaji to kana transliterator} (2007).}
	\resitem{\textit{B-Sides} art exhibition, Anderson Gallery, Des Moines, IA, USA (2005).}
	\resitem{Blended art with computer science by developing software that generates artistic images (2005).}
	\resitem{Manage a heterogeneous home network and servers (1997--present).}
	\resitem{Co-founded the \emph{Institute for Advanced Perpendicular Logic Studies} (1997).}
	\resitem{Received a National Merit Scholarship (1996).}
	\resitem{Awarded Eagle Scout Rank, Boy Scouts of America (1996).}

\end{ressection}


\end{document}
